An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-07-09 gas-adsorption/rsc-gas-ads-complete.tex
edit empirical study paragraph. and fix reference

A third body of work incorporated both gas-gas interactions \emph{and} steric
interactions of the gas with the atoms of the porous material. Simulations of
methane adsorption in hundreds of thousands of explicit nanoporous crystal
structures---both real and hypothetical---suggested that the ARPA-E deliverable
capacity target is infeasible~\cite{simon2015materials}; the highest simulated
methane deliverable capacity was 196 cm$^3$~STP/cm$^3$. Confidence in this
conclusion rests upon (i) the accuracy of the intermolecular potentials
describing the molecular interactions and (ii) the sufficient sampling of
material space, i.e.\ that the structures considered are representative of the
set of possible materials \cite{Moosavi2020}. To further explore material space and address
sensitivity to the intermolecular potentials: scaling the Lennard-Jones
potential well depths of material atoms to model enhanced
interactions~\cite{gomez2014exploring}, placing Lennard-Jones spheres in a unit
cell randomly to form ``pseudo-materials''~\cite{kaija2018high}, and generating
fictitious potential energy fields via a generative adversarial network trained
on zeolite structures~\cite{lee2019predicting} all generated model substrates
that failed to meet the ARPA-E methane deliverable capacity target.

\startreferees{Added discussion of screening studies}
Finally, a number of empirical studies have been performed that computationally
simulate an adsorption in a vast array of possible porous
structures~\cite{firlej2013understanding, goldsmith2013theoretical,
ahmed2019exceptional}.  Such studies can guide the development of new materials
by allowing researchers to identify commonalities among materials that have
desirable properties.  However, such an approach can only place a \emph{lower
bound} on the highest attainable deliverable capacity.

>>>>

A third body of work incorporated both gas-gas interactions \emph{and} steric
interactions of the gas with the atoms of the porous material. Simulations of
methane adsorption in hundreds of thousands of explicit nanoporous crystal
structures---both real and hypothetical---suggested that the ARPA-E deliverable
capacity target is infeasible~\cite{simon2015materials}; the highest simulated
methane deliverable capacity was 196 cm$^3$~STP/cm$^3$. Confidence in this
conclusion rests upon (i) the accuracy of the intermolecular potentials
describing the molecular interactions and (ii) the sufficient sampling of
material space, i.e.\ that the structures considered are representative of the
set of possible materials \cite{Moosavi2020understanding}. To further explore material space and address
sensitivity to the intermolecular potentials: scaling the Lennard-Jones
potential well depths of material atoms to model enhanced
interactions~\cite{gomez2014exploring}, placing Lennard-Jones spheres in a unit
cell randomly to form ``pseudo-materials''~\cite{kaija2018high}, and generating
fictitious potential energy fields via a generative adversarial network trained
on zeolite structures~\cite{lee2019predicting} all generated model substrates
that failed to meet the ARPA-E methane deliverable capacity target.

\startreferees{Added discussion of screening studies}
Finally, in a number of studies, molecular simulations of gas adsorption in
a large pool of both existing and predicted nanoporous
structures empirically shed light on performance limitations \cite{firlej2013understanding, goldsmith2013theoretical,
ahmed2019exceptional,simon2015materials}.
Such studies can guide the development of new materials
by allowing researchers to identify commonalities among materials that have
desirable properties.  
However, the largest observed simulated deliverable capacity among the pool of candidate materials in such studies
is only a \emph{lower bound} on the highest attainable deliverable capacity that is is predicted upon the accuracy of the molecular models.
\donereferees
